---
title: "Choices Modelling Experiment 4"
author: "Juan Carpio"
output: html_document
---

## Setting directory and relevant library
```{r,echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE, message=FALSE, warning=FALSE}

# Reading Clean File and setting relevant libraries.

## Change working directory
setwd("C:/Users/K56CA/Dropbox/PhD/Experiments Incentives/Follow_Up_Incentives/incentives-repo")

##Relevant libraries
library("nnet")# Multinomial regression
library("Hmisc")
library("dplyr")
library("tidyr")
library("ggplot2")
library("reshape2")
library("leaps")
library("car")
library("ordinal", lib.loc="~/R/win-library/3.2")

## read raw_data
data_clean_imp<-read.csv("clean_data_Exp4.csv")
## correcting ID veriable
data_clean<- mutate(data_clean_imp, ID= X+1) %>% 
        select(ID, everything(), -X)

```

## Preparing Data Frame
```{r,echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE}

##Define factor variables

data_clean$r_amount <- factor(data_clean$r_amount, levels = c(1,2),
                      labels = c("£2", "£5")) 

data_clean$r_type <- factor(data_clean$r_type, levels = c(1,2),
                    labels = c("Cash", "Product")) 

data_clean$gender <- factor(data_clean$gender, levels = c(1,2),
                    labels = c("Male", "Female"))

data_clean$income <- factor(data_clean$income, levels = c(1:5),
                    labels = c("< 15k", "15k-19k",
                               "20k-29k", "> 30k", "No.Ans")) 

data_clean$employ <- factor(data_clean$employ, levels = c(1:6),
                    labels = c("FT-Emp", "PT-Emp","Unempl.", 
                               "Stud.", "Retired","Other")) 

## Adding totals for Measures: Neg.Evaluations and Expectations 

expect_1<-c("exp_x1_K","exp_x1_T", "exp_x1_S.R","exp_x1_G")
expect_2<-c("exp_x2_K","exp_x2_T", "exp_x2_S.R","exp_x2_G")
expect_all<-c("exp_x1_K","exp_x1_T", "exp_x1_S.R","exp_x1_G",
              "exp_x2_K","exp_x2_T", "exp_x2_S.R","exp_x2_G")
neg_eval<-c("neg.ev_1","neg.ev_2.R","neg.ev_3","neg.ev_4.R",
            "neg.ev_5","neg.ev_6","neg.ev_7.R","neg.ev_8",
            "neg.ev_9","neg.ev_10.R", "neg.ev_11","neg.ev_12")

final_df<-data_clean %>% mutate(
        tot_exp1 = rowMeans(.[expect_1]),
        tot_exp2 = rowMeans(.[expect_2]),
        exp_all = rowMeans(.[expect_all]),
        tot_neg_eval = rowMeans(.[neg_eval])
        )  

#final_df %>% group_by(r_amount) %>% summarise(avg = mean(age))

# Code to audit cases ###################
# final_df %>% filter(ID==315) %>% gather()
#########################################

```



## Function to estimate the model

Takes a given multinomial model an return a table with all relevant values, including Likelihood Ratio test. 
```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE, results='hide'}

mod_frame <- function(m){
        
        mod<-summary(m)
        n<-length(mod$coefficients[1,])*2
   #Estimate Table values        
        coef<-matrix(cbind(mod$coefficients[1,],
                   mod$coefficients[2,]),n ,1)
        se<-matrix(cbind(mod$standard.errors[1,],
                 mod$standard.errors[2,]), n,1)
        z <-matrix(cbind(mod$coefficients[1,]/mod$standard.errors[1,],
                         mod$coefficients[2,]/mod$standard.errors[2,]))
        p <-((1 - pnorm(abs(z), 0, 1))*2)
        
        odds<- exp(coef)
       
        r.deviance<-mod$deviance
        AIC<-mod$AIC
        
        coef.name<-matrix(rep(mod$vcoefnames,2),n,1)
        cond<- matrix(cbind(rep(c("1_Friend"),n/2),
                        rep(c("2_Friends"),n/2)),n,1)
   #Build table        
                df<- as.data.frame(cbind(cond, coef.name)) %>% 
                cbind(round(cbind(coef,se,z,p,odds),3))
                colnames(df)<-c("Condition","Variable","Coeff",
                        "Sd.Error","z.value", "p.value", "odds")
                print(mod$call)
                print(df)

   #Model goodness of fitness
                fit<-(cbind(r.deviance,AIC))
                colnames(fit)<-c("Residual Deviance","AIC")
                print(fit)
   #Likelihood Ratio Test
                print(Anova(m))
}

```


# First Choice preferences Modelling 


### Exclude all terms whose elimination did not result in a significant reduction of the model fitness (Page 142-144)
```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE, message=FALSE, warning=FALSE}

# Preparing data
long_data<-melt(final_df, measure.var= c("vd_0f","vd_1f","vd_2f"),
        id.var = c("ID","r_type", "r_amount", "tot_neg_eval",
                   "tot_exp1","tot_exp2", "exp_all", "gender",
                   "income", "age", "employ")) 

mr_data<- filter(long_data, value==1)
mr_data[[3]]=as.factor(mr_data[[3]])


mod1<- multinom(variable ~ r_type + exp_all + income + 
                employ + r_amount + gender + tot_neg_eval
                ,data = mr_data)
mod2<-update(mod1, . ~ . - tot_neg_eval)
mod3<-update(mod2, . ~ . - gender)
mod4<-update(mod3, . ~ . - r_amount)
mod5<-update(mod4, . ~ . - employ)

#Additional models
mod6<-update(mod4, . ~ . - income)
mod7<-update(mod4, . ~ . - exp_all)

# "mod5 (Model 2 in Thesis) is the one retained, and contains the variables: Reward Framing, Expectations about Friend's Reactions, and Income.
mod_frame(mod5)

```


## Type II Test (Page 143-144)
### Calculate the LR by comparing a model that excluded each individual factor with a model that included all the other possible covariates

```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE, message=FALSE, warning=FALSE}

                                                     ## p value L.R. ##
mod1x<- multinom(variable ~ r_type, data = mr_data)      #  0.0126  *
mod2x<- multinom(variable ~ exp_all, data = mr_data)     #  0.1136  *
mod3x<- multinom(variable ~ income, data = mr_data)      #  0.03547 *
mod4x<- multinom(variable ~ employ, data = mr_data)      #  0.3815 
mod5x<- multinom(variable ~ r_amount, data = mr_data)    #  0.6254  
mod6x<- multinom(variable ~ gender, data = mr_data)      #  0.6475
mod7x<- multinom(variable ~ tot_neg_eval, data = mr_data)#  0.727 

# The variables: Reward Framing, Expectations about Friend's Reactions, and Income has the Lowest p values. 

```


## Selecting Final Model 
### Selection of final predictors by comparing the goodness of fitness of several models (Table 15)

```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE, message=FALSE, warning=FALSE}

                                                  ##Res.Dev.   AIC
m1<- update(mod5, .~. + r_amount)  #Model 3       #406.0627 438.0627
m2<- update(mod5, .~. + tot_neg_eval) #Model 4    #407.5776 439.5776
m3<- update(mod5, .~. + gender) #Model 5          #407.0715 439.0715
m4<- update(mod5, .~. + age)  #Model 6            #407.1102 439.1102
m5<- update(mod5, .~. + employ) #Model 7          #397.2083 445.2083
m6<- update(mod5, .~. + r_amount*exp_all)#Model 8 #393.9693 429.9693
m7<- update(mod5, .~. + r_amount + r_amount*exp_all) # ""      ""

#Model 11
m8<- update(mod5, .~. + r_amount*exp_all-income)  #409.1858 429.1858 
#Model 9
m9<- update(m6, .~. + r_amount*r_type)            #393.2482 433.2482
#Model 10
m12<- update(m6, .~.  + exp_all*r_type)           #390.9565 430.9565

#Models not considered in the Thesis
m10<- update(m6, .~. + r_amount*r_type -r_amount) #401.7075 437.7075
m11<- update(mod5, .~.  + r_amount*exp_all - r_amount)
                                                  #404.4128 436.4128

#############
#FINAL MODEL#
#############

#We selected m6 (Model 8) as our Final Model.- Table 16
mod_frame(m6)

```


# Probability Plots

##fitted model keeping "Income" constant, and comparing the "Reward amount" within each group (FIGURE 13 AND FIGURE 14)
```{r}

v.r_type<-c("Cash", "Product")
v.exp_all<-c(1:9)
v.r_amount<-c("£2", "£5")
v.income<- factor(1, levels = c(1),labels = c("< 15k"))

dexp<-expand.grid(v.r_type, v.exp_all, v.r_amount, v.income)
colnames(dexp)<-c("r_type", "exp_all", "r_amount", "income")


## store the predicted probabilities for each value of ses and write
pp.exp <- cbind(dexp, predict(m6, newdata = dexp, 
                               type = "probs", se = TRUE))

## calculate the mean probabilities within each level of ses
by(pp.exp[, 5:7], pp.exp$r_type, colMeans)

## melt data set to long for ggplot2
lpp <- melt(pp.exp, id.vars = c("exp_all", "r_type",
                "income", "r_amount"), value.name = "probability")

head(lpp) # view first few rows

## plot predicted probabilities across write values for
## each level of ses facetted by program type

lpp2 <- lpp
#Change schems labels
levels(lpp2$variable)[levels(lpp2$variable)=="vd_0f"]<- "No Friends"
levels(lpp2$variable)[levels(lpp2$variable)=="vd_1f"]<- "1 Friend"
levels(lpp2$variable)[levels(lpp2$variable)=="vd_2f"]<- "2 Friend2"
#Change income label
levels(lpp2$income)[levels(lpp2$income)=="< 15k"]<- "Income= < 15k"

#Change reward amount label
levels(lpp2$r_amount)[levels(lpp2$r_amount)=="£2"]<- "Reward= £2"
levels(lpp2$r_amount)[levels(lpp2$r_amount)=="£5"]<- "Reward= £5"

head(lpp2, 3)

ggplot(lpp2, aes(x = exp_all, y = probability, colour = r_type)) +
        geom_line(size=1) +
        facet_grid(variable ~ r_amount*income, scales="free")+
        scale_color_manual(values=c("blue","red"),
                name="Reward Framing") +
        scale_x_continuous(limits =c(1,9), breaks=seq(1,9,1))+
        labs(x="Expectations about friends reactions", 
                y="Choice probability")

ggplot(lpp2, aes(x = exp_all, y = probability, colour = r_amount)) +
        geom_line(size=1) +
        facet_grid(variable ~ r_type*income, scales="free")+
        scale_color_manual(values=c("blue","red"),
                name="Reward Amount") +
        scale_x_continuous(limits =c(1,9), breaks=seq(1,9,1))+
        labs(x="Expectations about friends reactions", 
                y="Choice probability")

 
```


## Estimated probabilities of the fitted model keeping                  "Expectations about Friends" constant. (FIGURE 15)

```{r}

v.r_type<-c("Cash", "Product")
v.exp_all<-c(7) #average value
v.r_amount<-c("£2", "£5")
v.income<- c("< 15k", "15k-19k","20k-29k", "> 30k", "No.Ans")

dexp<-expand.grid(v.r_type, v.exp_all, v.r_amount, v.income)
colnames(dexp)<-c("r_type", "exp_all", "r_amount", "income")


## store the predicted probabilities for each value of ses and write
pp.exp <- cbind(dexp, predict(m7, newdata = dexp, 
                               type = "probs", se = TRUE))

## calculate the mean probabilities within each level of ses
by(pp.exp[, 5:7], pp.exp$r_type, colMeans)

## melt data set to long for ggplot2
lpp <- melt(pp.exp, id.vars = c("exp_all", "r_type",
                "income", "r_amount"), value.name = "probability")

head(lpp) # view first few rows

## plot predicted probabilities across write values for
## each level of ses facetted by program type

lpp2 <- lpp
#Change schems labels
levels(lpp2$variable)[levels(lpp2$variable)=="vd_0f"]<- "No Friends"
levels(lpp2$variable)[levels(lpp2$variable)=="vd_1f"]<- "1 Friend"
levels(lpp2$variable)[levels(lpp2$variable)=="vd_2f"]<- "2 Friend2"

#Change reward amount label
levels(lpp2$r_amount)[levels(lpp2$r_amount)=="£2"]<- "Reward= £2"
levels(lpp2$r_amount)[levels(lpp2$r_amount)=="£5"]<- "Reward= £5"

head(lpp2, 3)


ggplot(lpp2, aes(x = income, y = probability,
                colour = r_type, group=r_type)) +
                geom_line()+
                geom_point() + 
                facet_grid(variable ~ r_amount, scales="free")+
                        scale_color_manual(values=c("blue","red"),
                        name="Reward Type") +
                theme(axis.text.x= element_text(angle = 90, hjust= 1))+
                labs(x="Income Category", y="Choice probability")
 
```
