---
title: "Exloratory and Inferential Analysis - Experiment 4"
author: "Juan Carpio"
output: html_document
---

## Setting directory and relevant library
```{r,echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE, results='hide', warning=FALSE, message=FALSE}
# Reading Clean File and setting relevant libraries.

## Change working directory
setwd("C:/Users/K56CA/Dropbox/PhD/Experiments Incentives/Follow_Up_Incentives/incentives-repo")

##Relevant libraries
library("Hmisc")
library("plyr")
library("dplyr")
library("tidyr")
library("ggplot2")
library("reshape2")
library("leaps")
library("car")
library("ordinal", lib.loc="~/R/win-library/3.2")

```

## Preparing data frame for analysis

```{r,echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE, results='hide', warning=FALSE, message=FALSE}

## read raw_data
data_clean_imp<-read.csv("clean_data_Exp4.csv")
## correcting ID veriable
data_clean<- mutate(data_clean_imp, ID= X+1) %>% 
        select(ID, everything(), -X)

##Define factor variables

data_clean$r_amount <- factor(data_clean$r_amount, levels = c(1,2),
                      labels = c("£2", "£5")) 

data_clean$r_type <- factor(data_clean$r_type, levels = c(1,2),
                    labels = c("Cash", "Product")) 

data_clean$gender <- factor(data_clean$gender, levels = c(1,2),
                    labels = c("Male", "Female"))

data_clean$income <- factor(data_clean$income, levels = c(1:5),
                    labels = c("< 15k", "15k-19k",
                               "20k-29k", "> 30k", "No.Ans")) 

data_clean$employ <- factor(data_clean$employ, levels = c(1:6),
                    labels = c("FT-Emp", "PT-Emp","Unempl.", 
                               "Stud.", "Retired","Other")) 


## Adding totals for Measures: Neg.Evaluations and Expectations 

expect_1<-c("exp_x1_K","exp_x1_T", "exp_x1_S.R","exp_x1_G")
expect_2<-c("exp_x2_K","exp_x2_T", "exp_x2_S.R","exp_x2_G")
expect_all<-c("exp_x1_K","exp_x1_T", "exp_x1_S.R","exp_x1_G",
              "exp_x2_K","exp_x2_T", "exp_x2_S.R","exp_x2_G")
neg_eval<-c("neg.ev_1","neg.ev_2.R","neg.ev_3","neg.ev_4.R",
            "neg.ev_5","neg.ev_6","neg.ev_7.R","neg.ev_8",
            "neg.ev_9","neg.ev_10.R", "neg.ev_11","neg.ev_12")

final_df<-data_clean %>% mutate(
        tot_exp1 = rowMeans(.[expect_1]),
        tot_exp2 = rowMeans(.[expect_2]),
        exp_all = rowMeans(.[expect_all]),
        tot_neg_eval = rowMeans(.[neg_eval])
        )  

#final_df %>% group_by(r_amount) %>% summarise(avg = mean(age))

# Code to audit cases ###################
# final_df %>% filter(ID==315) %>% gather()
#########################################

```


## Chi Square Preferences First Choice (page 140)

More than 80% prefered not to share the rward with anyone as a first choice. Such difference was highly significant. 
```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE, warning=FALSE, message=FALSE}

long_data<-melt(final_df, measure.var= c("vd_0f","vd_1f","vd_2f"),
        id.var = c("ID","r_type", "r_amount", "tot_neg_eval",
                   "tot_exp1","tot_exp2", "exp_all")) 

chi_data<- filter(long_data, value==1)

#Summarise first choice frequencies and proportions
fr<-as.matrix(table(chi_data$variable))
p <- c(fr[1,1]/nrow(chi_data), fr[2,1]/nrow(chi_data),
                fr[3,1]/nrow(chi_data)) 

#calculating chi square
fr
p
chisq.test(fr)

```


# Scheme Ranking and Reward Amount (Section 3.3.2)

## Reward Amount and Expectations Sharing with 1 FRIEND 

### Mann Witney Test

```{r,echo=TRUE, eval=TRUE, include=TRUE, cache=TRUE, warning=FALSE, message=FALSE}


low.exp_df<-final_df %>% filter(tot_exp1 <= 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_amount)

high.exp_df<-final_df %>% filter(tot_exp1 > 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_amount)


u.low<-lapply(low.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~low.exp_df[,4],var.equal= TRUE))
u.low
u.high<-lapply(high.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~high.exp_df[,4],var.equal= TRUE))
u.high

```

### FIGURE 16: Ranking, Reward Amount and Expectations Sharing with 1 FRIEND
```{r}
data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("r_type", "r_amount", "exp_all"))

dd<-data %>%  mutate(catg = ifelse(exp_all < 4.5, "Negative Expectations","Positive Expectations"))


pct <- data %>% 
  group_by(variable,r_amount,value) %>% 
  summarise(n=n()) %>% 
  group_by(variable) %>% 
  mutate(perc=100*n/sum(n))

pct$variable <- factor(pct$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))

names(pct)[2]<-"Reward"

## BY EXPECTATION CATEGORY SEPARATING EXPECTATIONS
data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("r_type", "r_amount", "tot_exp1", "tot_exp2"))

exp_df<-data %>% mutate(cat.exp1 = ifelse(tot_exp1 < 4.5, 
                "Low Expecations","High Expectations"),
                        cat.exp2 = ifelse(tot_exp2 < 4.5, 
                "Low Expectations","High Expectations"))
exp_df$variable <- factor(exp_df$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))

# Expectations sharing with one friend
avg_rank1<-exp_df %>% group_by(variable,r_amount, cat.exp1) %>%
        summarise(rank=mean(value))
names(avg_rank1)[2]<-c("Amount")

ggplot(avg_rank1, aes(x=Amount, y=rank, fill=Amount) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid( cat.exp1~ variable )+
        scale_fill_brewer(palette="Set1")+
        scale_y_continuous(limits =c(0,3), breaks=seq(0,3, 0.5))+
        theme_bw()+
        labs(x="Reward Amount", y="Average Ranking")
```

## Reward Amount and Expectations Sharing with 2 FRIENDS  

### Mann Witney Test 
 
```{r,echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE, warning=FALSE, message=FALSE}


low.exp_df<-final_df %>% filter(tot_exp2 <= 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_amount)

high.exp_df<-final_df %>% filter(tot_exp2 > 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_amount)


u.low.2f<-lapply(low.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~low.exp_df[,4],var.equal= TRUE))
u.low.2f
u.high.2f<-lapply(high.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~high.exp_df[,4],var.equal= TRUE))
u.high.2f
```

### FIGURE 17: Ranking, Reward Amount and Expectations Sharing with 2 FRIENDS
```{r}
data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("r_type", "r_amount", "exp_all"))

dd<-data %>%  mutate(catg = ifelse(exp_all < 4.5, "Negative Expectations","Positive Expectations"))


pct <- data %>% 
  group_by(variable,r_amount,value) %>% 
  summarise(n=n()) %>% 
  group_by(variable) %>% 
  mutate(perc=100*n/sum(n))

pct$variable <- factor(pct$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))

names(pct)[2]<-"Reward"

## BY EXPECTATION CATEGORY SEPARATING EXPECTATIONS
data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("r_type", "r_amount", "tot_exp1", "tot_exp2"))

exp_df<-data %>% mutate(cat.exp1 = ifelse(tot_exp1 < 4.5, 
                "Low Expecations","High Expectations"),
                        cat.exp2 = ifelse(tot_exp2 < 4.5, 
                "Low Expectations","High Expectations"))
exp_df$variable <- factor(exp_df$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))

# Expectations sharing with two friends
avg_rank2<-exp_df %>% group_by(variable,r_amount, cat.exp2) %>%
        summarise(rank=mean(value))
names(avg_rank2)[2]<-c("Amount")

ggplot(avg_rank2, aes(x=Amount, y=rank, fill=Amount) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid( cat.exp2~ variable )+
        scale_fill_brewer(palette="Set1")+
        scale_y_continuous(limits =c(0,3), breaks=seq(0,3, 0.5))+
        theme_bw()+
        labs(x="Reward Amount", y="Average Ranking")
```


# Reward Amount and expectations about friends' reactions (Section 3.3.3) 

### Mann Whitney test
```{r,echo=TRUE, eval=TRUE, include=TRUE, cache=TRUE, warning=FALSE, message=FALSE}

#Median
final_df %>% select(tot_exp1, tot_exp2, r_amount) %>%
                group_by(r_amount) %>%
                summarise(median(tot_exp1),median(tot_exp2), 
                          mean(tot_exp1),mean(tot_exp2))

# Mann Whitney U-Test
u<-lapply(final_df[,c(31:33)], 
          function(x) wilcox.test(x ~ final_df[,29], var.equal= FALSE))
u

```

### FIGURE 18: Plot Reward Amount and Expectations Friends Reactions
```{r,echo=TRUE, eval=TRUE, include=TRUE, cache=TRUE, warning=FALSE, message=FALSE}

gdata<-melt(final_df, measure.var= c("tot_exp1", "tot_exp2" ), 
         id.var = c("r_type", "r_amount"))

gdata$variable <- factor(gdata$variable,
                labels = c("1 Friend", 
                          "2 Friends"))
names(gdata)[2]<-"Reward"


ggplot(gdata, aes(x=variable, y=value, fill=Reward))+
        geom_bar(stat = "summary", fun.y = "mean",position="dodge")+
        scale_y_continuous(limits =c(0,9), breaks=seq(0,9,1))+
        scale_fill_brewer(palette="Set1")+
        labs(x="Number of friends with which the reward would be shared",
                y="Score-Expectations about friend's reaction")+
        theme_bw()
```

# Scheme Ranking and Reward Framing (Section 3.3.4)

Significant differences were found in terms of the type of reward (Cash or product) among the participants who preferred to share their reward (minority). 


### Means and Mann Whitney Test
```{r,echo=TRUE, eval=TRUE, include=TRUE, cache=TRUE}

#Means
final_df %>% select(vd_0f, vd_1f, vd_2f, r_type) %>%
                group_by(r_type) %>%
                summarise(mean(vd_0f),mean(vd_1f),mean(vd_2f))                  
# Mann Whitney U-Test
u<-lapply(final_df[,c(2:4)], 
          function(x) wilcox.test(x ~ final_df[,30], var.equal= FALSE))

u
```

### FIGURE 19: Average ranking of each incentive scheme comparing the "Reward Framing".
```{r,echo=TRUE, eval=TRUE, include=TRUE, cache=TRUE}

data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("r_type", "r_amount", "tot_exp1", "tot_exp2"))

avg_rank<-data %>% group_by(variable,r_type) %>%
        summarise(rank=mean(value))

avg_rank$variable <- factor(avg_rank$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))
names(avg_rank)[2]<-c("Framing")

ggplot(avg_rank, aes(x=Framing, y=rank, fill=Framing) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid(~ variable)+
        scale_fill_brewer(palette="Set1")+
        scale_y_continuous(limits =c(0,3), breaks=seq(0,3, 0.5))+
        theme_bw()+
        labs(x="Reward Framing", y="Average Ranking")
```


## Reward Framing and Expectations Sharing with 1 FRIEND  

### Mann Whitney Test
```{r,echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE, warning=FALSE}

low.exp_df<-final_df %>% filter(tot_exp1 <= 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_type)

high.exp_df<-final_df %>% filter(tot_exp1 > 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_type)


u.low.1f<-lapply(low.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~low.exp_df[,4],var.equal= TRUE))
u.low.1f
u.high.1f<-lapply(high.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~high.exp_df[,4],var.equal= TRUE))
u.high.1f
```

### FIGURE 20: Average ranking comparing the "Reward Framing", based on the expectations about sharing the reward with ONE friend.

```{r,echo=TRUE, eval=TRUE, include=TRUE, cache=TRUE}

exp_df<-data %>% mutate(cat.exp1 = ifelse(tot_exp1 < 4.5, 
                "Low Expecations","High Expectations"),
                        cat.exp2 = ifelse(tot_exp2 < 4.5, 
                "Low Expectations","High Expectations"))
exp_df$variable <- factor(exp_df$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))

# Expectations sharing with one friend (FIGURE 20)
avg_rank1<-exp_df %>% group_by(variable,r_type, cat.exp1) %>%
        summarise(rank=mean(value))
names(avg_rank1)[2]<-c("Framing")

ggplot(avg_rank1, aes(x=Framing, y=rank, fill=Framing) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid( cat.exp1~ variable )+
        scale_fill_brewer(palette="Set1")+
        scale_y_continuous(limits =c(0,3), breaks=seq(0,3, 0.5))+
        theme_bw()+
        labs(x="Reward Amount", y="Average Ranking")
```


## Reward Framing and Expectations Sharing with 2 FRIENDS

### Mann Whitney Test
```{r,echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE, warning=FALSE}


low.exp_df<-final_df %>% filter(tot_exp2 <= 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_type)

high.exp_df<-final_df %>% filter(tot_exp2 > 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_type)


u.low.2f<-lapply(low.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~low.exp_df[,4],var.equal= TRUE))
u.low.2f
u.high.2f<-lapply(high.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~high.exp_df[,4],var.equal= TRUE))
u.high.2f
```

### FIGURE 21: Average ranking comparing the "Reward Framing", based on the expectations about sharing the reward with TWO friends.

```{r,echo=TRUE, eval=TRUE, include=TRUE, cache=TRUE}

exp_df<-data %>% mutate(cat.exp1 = ifelse(tot_exp1 < 4.5, 
                "Low Expecations","High Expectations"),
                        cat.exp2 = ifelse(tot_exp2 < 4.5, 
                "Low Expectations","High Expectations"))
exp_df$variable <- factor(exp_df$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))

# Expectations sharing with two friends (FIGURE 21)
avg_rank2<-exp_df %>% group_by(variable,r_type, cat.exp2) %>%
        summarise(rank=mean(value))
names(avg_rank2)[2]<-c("Framing")

ggplot(avg_rank2, aes(x=Framing, y=rank, fill=Framing) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid( cat.exp2~ variable )+
        scale_fill_brewer(palette="Set1")+
        scale_y_continuous(limits =c(0,3), breaks=seq(0,3, 0.5))+
        theme_bw()+
        labs(x="Reward Amount", y="Average Ranking")

```


# Reward Framing and expectations about friends'  (Section 3.3.5)

### Mann Whitney Test and Median
```{r,echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

#Median
final_df %>% select(tot_exp1, tot_exp2, r_type) %>%
                group_by(r_type) %>%
                summarise(median(tot_exp1),median(tot_exp2), 
                          mean(tot_exp1),mean(tot_exp2))

# Mann Whitney U-Test
u<-lapply(final_df[,c(31:33)], 
          function(x) wilcox.test(x ~ final_df[,30], var.equal= FALSE))
ps<-data.frame(p.value = sapply(u, getElement, name = "p.value"))
format(ps, scientific = TRUE)

```

### FIGURE 22: Differences between "Reward Framing" in terms of expectations about sharing the reward with either one or two friends.

```{r,echo=TRUE, eval=TRUE, include=TRUE, cache=TRUE}
gdata<-melt(final_df, measure.var= c("tot_exp1", "tot_exp2" ), 
         id.var = c("r_type", "r_amount"))

gdata$variable <- factor(gdata$variable,
                labels = c("1 Friend", 
                          "2 Friends"))
names(gdata)[1]<-"Framing"


ggplot(gdata, aes(x=variable, y=value, fill=Framing))+
        geom_bar(stat = "summary", fun.y = "mean",position="dodge")+
        scale_y_continuous(limits =c(0,9), breaks=seq(0,9,1))+
        scale_fill_brewer(palette="Set1")+
        labs(x="Number of friends with which the reward would be shared",
                y="Score-Expectations about friend's reaction")+
        theme_bw()

```

# Interaction between Reward Framing and Reward Amount (Section 3.3.6)
```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

gdata<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("r_type", "r_amount"))

avg_rank<-gdata %>% group_by(variable,r_type, r_amount) %>%
        summarise(rank=mean(value))

avg_rank$variable <- factor(avg_rank$variable,
                     labels = c("NO Friend", "1 Friend", "2 Friends"))
names(avg_rank)[2]<-"Framing"
names(avg_rank)[3]<-"Amount"

#amount * Type

ggplot(avg_rank, aes(x=Amount, y=rank, fill=Amount) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid(variable ~ Framing)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        scale_y_continuous(limits =c(0,3), breaks=seq(0,3, 1))+
        labs(x="Reward Framing", y="Average Ranking")

```

# Fears of negatives evaluations, AGE and GENDER (Section 3.3.7)
Younger people and Females have a tendency to have higher fears of Negative Evaluations. 

### Mann Whitney Test and Correlations
```{r,echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

# Mann Whitney U-Test Reward Amount
t.test(final_df[,34] ~ final_df[,29], var.equal= FALSE)
# Mann Whitney U-Test Reward Type
t.test(final_df[,34] ~ final_df[,30], var.equal= FALSE)
# Mann Whitney U-Test Gender
t.test(final_df[,34] ~ final_df[,25], var.equal= FALSE)

#Correlation
rcorr(final_df[,34], final_df[,27], type="pearson")  
```

### FIGURE 24: Relationship between age and the Fears of Negative Evaluations scale,

```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=FALSE}

ggplot(final_df, aes(x=tot_neg_eval, y=age, color=gender)) +
        geom_point(shape=16, size = I(5), alpha = I(0.5)) +
        scale_color_manual(values=c('blue','red'))+
        geom_smooth(method=lm,size=2, se=FALSE) +
        labs(x="Scale - Fears of Negative Evaluations", y="Age")+
        scale_y_continuous(limits =c(10,90), breaks=seq(10,90,10))+
        theme_bw()

```

### Mediations Analysis FNE and Expectations about friends' reactions

```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE}
long_data<-melt(final_df, measure.var= c("vd_0f","vd_1f","vd_2f"),
        id.var = c("ID","r_type", "r_amount", "tot_neg_eval",
                   "tot_exp1","tot_exp2", "exp_all", "gender",
                   "income", "age", "employ")) 

mr_data<- filter(long_data, value==1)
mr_data[[3]]=as.factor(mr_data[[3]])

mediation1<-lm(tot_neg_eval~tot_exp1, data = mr_data)
mediation2<-lm(tot_neg_eval~tot_exp2, data = mr_data)
summary (mediation1)
summary (mediation2)
```


# Expectations about Friends' Reaction in general (Section 3.3.8)

### Mann Whitney Test and Means
```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE}

gdata<-melt(final_df, measure.var= c("tot_exp1", "tot_exp2"), 
         id.var = c("gender"))

#Median and Mean per number of friends
gdata %>% group_by(variable) %>%
        summarise(median(value),mean(value))

#Median and Mean per Gender
gdata %>% group_by(gender) %>%
        summarise(median(value),mean(value))

# Mann Whitney between number of friends
wilcox.test(gdata[,3] ~ gdata[,2], var.equal= FALSE)

# Mann Whitney between GENDER

lapply(final_df[,c(31:32)], 
          function(x) wilcox.test(x ~ final_df[,25], var.equal= FALSE))


```

### FIGURE 25: Differences between "Genders" in terms of expectations about sharing the reward with either one or two friends.

```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE}

gdata$variable <- factor(gdata$variable, 
                     labels = c("Exp. Sharing with 1 Friend", 
                                "Exp. Sharing with 2 Friends"))
names(gdata)[1]<-"Gender"

ggplot(gdata, aes(x=Gender, y=value, fill=Gender) )+
        geom_bar(stat = "summary", fun.y = "mean",position="dodge")+
        facet_grid(. ~ variable)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        coord_cartesian(ylim=c(0, 8.5))+
        scale_y_continuous(limits =c(0,9), breaks=seq(0,9, 1))+
        labs(x="Gender", 
             y="Score-Expectations about friends' reactions")

```

# Income and schemes' preferences (Section 3.3.9)

### Mann Whitney Test
```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=FALSE}

# Mann Whitney between income categories

lapply(final_df[,c(2:4)], 
          function(x) kruskal.test(x~ final_df[,26]))

```

### FIGURE 26: Income categories and schemes' average rankings.
```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE}

data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("income"))

avg_rank<-data %>% group_by(variable,income) %>%
        summarise(rank=mean(value))

avg_rank$variable <- factor(avg_rank$variable,
                     labels = c("NO Friend", "1 Friend", "2 Friends"))
names(avg_rank)[2]<-"Income"

ggplot(avg_rank, aes(x=Income, y=rank, fill=Income) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid(~ variable)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+
        labs(x="Income Category", y="Average Ranking")
```

### FIGURE 27: Income categories and expectations about friends' reactions.
```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=TRUE}

data<-melt(final_df, measure.var= c("tot_exp1", "tot_exp2"), 
         id.var = c("income"))


data$variable <- factor(data$variable,
                     labels = c("Exp. Sharing with 1 Friend", 
                                "Exp. Sharing with 2 Friends"))
names(avg_rank)[2]<-"Income"

ggplot(data, aes(x=income, y=value, fill=income) )+
        geom_bar(stat = "summary", fun.y = "mean",position="dodge")+
        facet_grid(~ variable)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+
        #scale_y_continuous(limits =c(0,6), breaks=seq(0,6, 1))+
        labs(x="Income Category", y="Expectations about friends' reactions")

```

### Correlations
```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE, warning=FALSE}

data<- final_df %>% select(vd_0f,vd_1f,vd_2f,tot_exp1,tot_exp2,income)                 %>% filter(income!="No.Ans") %>% 
                melt(measure.var= c("vd_0f","vd_1f","vd_2f"), 
                id.var = c("income","tot_exp1","tot_exp2")) %>%
                filter(value==1) %>%
                melt(measure.var= c("tot_exp1","tot_exp2"), 
                id.var = c("income", "variable")) 

names(data) <- c("income", "scheme", "exp.cat", "exp.value")
data$income <- as.numeric(data$income)

# Calculate correlation for each group

## Corralatuions value
ddply(data, c("exp.cat","scheme"), summarise, cor = round(cor(income, exp.value, method="spearman"), 4))

## p  value
ddply(data, c("exp.cat","scheme"), summarise, p = round(cor.test(income, exp.value, method="spearman")$p.value,4))

```

# ADDITIONAL ANALYSIS 

## ALPHA FNE and Expectations scales.
```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE, warning=FALSE, message=FALSE}

library("psych")

## Expectations about friends reactons
f1<-final_df %>% select(exp_x1_K, exp_x1_T, exp_x1_S.R, exp_x1_G) 
alpha(as.data.frame(f1))

f2<-final_df %>% select(exp_x2_K, exp_x2_T, exp_x2_S.R, exp_x2_G) 
alpha(as.data.frame(f2))

## Fears of Negative evaluations scale.
fne<- final_df %>% 
                select(neg.ev_1,neg.ev_2.R,neg.ev_3,
                neg.ev_4.R,neg.ev_5,neg.ev_6,neg.ev_7.R,
                neg.ev_8,neg.ev_9,neg.ev_10.R,neg.ev_11, neg.ev_12)
alpha(as.data.frame(fne))
```

## Explorations not included in Thesis

### Correlations Matrix

***
The strongest and most relevant correlations were between:

* Expect.Reaction_1 Friend -- Gender (-)
* Expect.Reaction_2 Friends -- Gender (-)
* Expect.Reaction_2 Friends -- Choice not sharing with Friends (-)
* Expect.Reaction_2 Friends -- Choice sharing with 2 Friends (+)
* Expect.Reaction_tOTAL -- Choice not sharing with Friends (-)
* Fear Neg. Evaluation -- Gender (+)
* Fear Neg. Evaluation -- Age (-)
***


####- Pearson
```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=FALSE}

rxy<- select(final_df, tot_exp1,tot_exp2,exp_all, tot_neg_eval, 
           vd_0f, vd_2f, vd_1f, gender, income, age, employ)

rxy[1:ncol(rxy)] <- lapply(rxy[1:ncol(rxy)], function(x) as.numeric(x))

rxy<-as.matrix(rxy) 
rcorr(rxy, type="pearson")                           
```
####- Spearman
```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=TRUE}
rxy<- select(final_df, tot_exp1,tot_exp2,exp_all,tot_neg_eval, 
            vd_0f, vd_2f, vd_1f, gender, income, age, employ)

rxy[1:ncol(rxy)] <- lapply(rxy[1:ncol(rxy)], function(x) as.numeric(x))

rxy<-as.matrix(rxy)   
rcorr(rxy, type="spearman")                           
```

### Employment / Scheme preferences
```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=TRUE}

data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("employ"))

fr1 <- data %>% 
        group_by(variable,employ,value) %>% 
        summarise(n=n()) 
fr2 <- fr1 %>% 
        group_by(employ, variable) %>% 
        summarise(n=sum(n))
pct <- left_join(fr1, fr2, by = c("employ"="employ", 
                                  "variable"="variable")) %>%
        mutate(perc=100*n.x/(n.y)) 


pct$variable <- factor(pct$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))
pct$value <- factor(pct$value)

names(pct)[2]<-"employ"

ggplot(pct, aes(x=value, y=perc, fill=variable) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid(~ employ)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        labs(x="Schemes Rankings", y="Percentage from the total of each alternative")

```


### Income / Scheme preferences
```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=TRUE}

data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("income"))


fr1 <- data %>% 
        group_by(variable,income,value) %>% 
        summarise(n=n()) 
fr2 <- fr1 %>% 
        group_by(income, variable) %>% 
        summarise(n=sum(n))
pct <- left_join(fr1, fr2, by = c("income"="income", 
                                  "variable"="variable")) %>%
        mutate(perc=100*n.x/(n.y)) 

pct$variable <- factor(pct$variable, 
                labels = c("NO Friend", "1 Friend", "2 Friends"))
pct$value <- factor(pct$value) 

names(pct)[2]<-"income"

ggplot(pct, aes(x=value, y=perc, fill=variable) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid(~ income)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        labs(x="Schemes Rankings", y="Percentage from the total of each alternative")

```

### Income / Scheme preferences (AVERAGE RANKING)
```{r, echo=TRUE, eval=TRUE, include=TRUE, cache=TRUE}

data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("income"))

avg_rank<-data %>% group_by(variable,income) %>%
        summarise(rank=mean(value))


ggplot(avg_rank, aes(x=variable, y=rank, fill=variable) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid(~ income)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        labs(x="Schemes Rankings", y="Percentage from the total of each alternative")

```


