---
title: "Incentives Exploratory Analysis"
author: "Juan Carpio"
date: "15 January 2016"
output: html_document
---

```{r,echo=FALSE, eval=TRUE, include=FALSE, cache=FALSE}
# Reading Clean File and setting relevant libraries.

## Change working directory
setwd("C:/Users/K56CA/Dropbox/PhD/Experiments Incentives/Follow_Up_Incentives")

##Relevant libraries

library("Hmisc")
library("dplyr")
library("tidyr")
library("ggplot2")
library("reshape2")
library("leaps")


## read raw_data
data_clean_imp<-read.csv("clean_data.csv")
## correcting ID veriable
data_clean<- mutate(data_clean_imp, ID= X+1) %>% 
        select(ID, everything(), -X)

##Define factor variables

data_clean$r_amount <- factor(data_clean$r_amount, levels = c(2,1),
                      labels = c("£5", "£2")) 

data_clean$r_type <- factor(data_clean$r_type, levels = c(1,2),
                    labels = c("Cash", "Product")) 

data_clean$gender <- factor(data_clean$gender, levels = c(1,2),
                    labels = c("Male", "Female"))

data_clean$income <- factor(data_clean$income, levels = c(1:5),
                    labels = c("< 15k", "15k-19k",
                               "20k-29k", "> 30k", "No.Ans")) 

data_clean$employ <- factor(data_clean$employ, levels = c(1:6),
                    labels = c("FT-Emp", "PT-Emp","Unempl.", 
                               "Stud.", "Retired","Other")) 

## Adding totals for Measures: Neg.Evaluations and Expectations 

expect_1<-c("exp_x1_K","exp_x1_T", "exp_x1_S.R","exp_x1_G")
expect_2<-c("exp_x2_K","exp_x2_T", "exp_x2_S.R","exp_x2_G")
expect_all<-c("exp_x1_K","exp_x1_T", "exp_x1_S.R","exp_x1_G",
              "exp_x2_K","exp_x2_T", "exp_x2_S.R","exp_x2_G")
neg_eval<-c("neg.ev_1","neg.ev_2.R","neg.ev_3","neg.ev_4.R",
            "neg.ev_5","neg.ev_6","neg.ev_7.R","neg.ev_8",
            "neg.ev_9","neg.ev_10.R", "neg.ev_11","neg.ev_12")

final_df<<-data_clean %>% mutate(
        tot_exp1 = rowMeans(.[expect_1]),
        tot_exp2 = rowMeans(.[expect_2]),
        exp_all = rowMeans(.[expect_all]),
        tot_neg_eval = rowMeans(.[neg_eval])
        )  

final_df %>% group_by(r_amount) %>% summarise(avg = mean(age))
# Code to audit cases ###################
# final_df %>% filter(ID==90) %>% gather()
#########################################

```

### Choices summary (Dependent variable)
`r round(338/401, 2)*100`% of the participants preferred to keep the entire reward for themselves (different from previous experiments). 
```{r, echo=FALSE, cache=TRUE}
tot_choices<-cbind(count(final_df, c(vd_0f)), count(final_df, c(vd_1f)),count(final_df, c(vd_2f)))
tot_choices
```

#1- SIZE OF THE REWARD (£2 vs 5£)
There are significant differences in the expectations about friends reactions depending on the SIZE OF THE REWARD to be shared.

### 1.1-FUNCTION calculating t.tests comparing AMOUNT size
```{r , echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

t<-lapply(final_df[,c(2:12,31:34)], 
          function(x) t.test(x ~ final_df[,29], var.equal = TRUE))

ps<-data.frame(p.value = sapply(t, getElement, name = "p.value"))
format(ps, scientific = FALSE)
           
```

### 1.2a-FUNCTION calculating Mann-Whitney (Non-Parametric) comparing AMOUNT (size)
```{r , echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

u<-lapply(final_df[,c(2:12,31:34)], 
          function(x) wilcox.test(x ~ final_df[,29], var.equal= FALSE))

ps<-data.frame(p.value = sapply(u, getElement, name = "p.value"))
format(ps, scientific = FALSE) 

```

### 1.3.a-Expectations about friends reactions and reward AMOUNT.
Expectations are more negatives when sharing the reward with two friends and when the reward is smaller.

```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}


gdata<-melt(final_df, measure.var= c("tot_exp1", "tot_exp2" ), 
         id.var = c("r_type", "r_amount"))

gdata$variable <- factor(gdata$variable,
                labels = c("1 Friend", "2 Friends"))
names(gdata)[2]<-"Reward"

ggplot(gdata, aes(x=variable, y=value, fill=Reward))+
        geom_boxplot(size = .75, position="dodge") +
        geom_jitter(alpha = .5)+
        scale_y_continuous(limits =c(0,9.1), breaks=seq(0,9, 0.5))+
        scale_fill_brewer(palette="Set1")+
        labs(x="Numbers of Friends to share the reward with", 
                y="Score-Expectations about friend's reaction")+
        theme_bw()

#dev.copy(jpeg,"figures/prueba2.jpeg")
#dev.off()
```

### 1.3.b-Expectations about friends reactions and reward AMOUNT.
Expectations are more negatives when sharing the reward with two friends and when the reward is smaller.

```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}


gdata<-melt(final_df, measure.var= c("tot_exp1", "tot_exp2" ), 
         id.var = c("r_type", "r_amount"))

gdata$variable <- factor(gdata$variable,
                labels = c("1 Friend", 
                          "2 Friends"))
names(gdata)[2]<-"Reward"

ggplot(gdata, aes(x=variable, y=value, fill=Reward))+
        stat_summary(fun.y="mean", geom="bar", position="dodge")+
        #geom_jitter(alpha = .5)+
        scale_y_continuous(limits =c(0,8), breaks=seq(0,8,.5))+
        scale_fill_brewer(palette="Set1")+
        labs(x="Numbers of friends with which the reward would be shared", 
                y="Score-Expectations about friend's reaction")+
        theme_bw()


ggplot(gdata, aes(x=variable, y=value, fill=Reward))+
        geom_boxplot(size = .75, position="dodge") +
        scale_y_continuous(limits =c(0,9.5), breaks=seq(0,10,1))+
        scale_fill_brewer(palette="Set1")+
        labs(x="Numbers of friends with which the reward would be shared",
                y="Score-Expectations about friend's reaction")+
        theme_bw()


#####

gdata$variable <- factor(gdata$variable,
                labels = c("1 Friend", "2 Friends"))
names(gdata)[2]<-"Reward"

ggplot(gdata, aes(x=variable, y=value, fill=Reward))+
        geom_boxplot(size = .75, position="dodge") +
        geom_jitter(alpha = .5)+
        scale_y_continuous(limits =c(0,9.1), breaks=seq(0,9, 0.5))+
        #coord_cartesian(ylim=c(0, 4.5))+
        scale_fill_brewer(palette="Set1")+
        labs(x="Numbers of Friends to share the reward with", 
                y="Score-Expectations about friend's reaction")+
        theme_bw()

ggplot(gdata, aes(x=variable, y=value, fill=variable))+
        geom_boxplot(size = .75, position="dodge") +
        geom_jitter(alpha = .2)+
        scale_y_continuous(limits =c(0,9.1), breaks=seq(0,9, 0.5))+
        scale_fill_brewer(palette="Set1")+
        facet_grid(~ Reward)+
        labs(x="Numbers of Friends to share the reward with", 
                y="Score-Expectations about friend's reaction")+
        theme_bw()

#dev.copy(jpeg,"figures/prueba2.jpeg")
#dev.off()
```


The next two plots show that the differences in terms of friend's expectations were only observed between REWARD AMOUNT but not in terms of TYPE OF REWARD.

### 1.4-Scheme rankings and reward AMOUNT.
No clear differences between preferences for sharing or not and the SIZE (amount) of the REWARD.

```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("r_type", "r_amount", "exp_all"))

dd<-data %>%  mutate(catg = ifelse(exp_all < 4.5, "Negative Expectations","Positive Expectations"))


pct <- data %>% 
  group_by(variable,r_amount,value) %>% 
  summarise(n=n()) %>% 
  group_by(variable) %>% 
  mutate(perc=100*n/sum(n))

pct$variable <- factor(pct$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))

names(pct)[2]<-"Reward"

ggplot(pct, aes(x=value, y=perc, fill=Reward) )+
        geom_bar(stat="identity",position="dodge")+
        ylab("percent") + 
        facet_grid(~ variable)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        labs(x="Schemes Ranking", y="Percentage from the total of each alternative")

#####


## AVERAGE RANKING

avg_rank<-data %>% group_by(variable,r_amount) %>%
        summarise(rank=mean(value))

ggplot(avg_rank, aes(x=r_amount, y=rank, fill=r_amount) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid(~ variable)+
        scale_fill_brewer(palette="Set1")+
        scale_y_continuous(limits =c(0,3), breaks=seq(0,3, 0.5))+
        theme_bw()+
        labs(x="Reward Amount", y="Average Ranking")

## BY EXPECTATION CATEGORY

avg_rank2<-dd %>% group_by(variable,r_amount, catg) %>%
        summarise(rank=mean(value))

avg_rank2$variable <- factor(avg_rank2$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))

ggplot(avg_rank2, aes(x=r_amount, y=rank, fill=r_amount) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid( catg~ variable )+
        scale_fill_brewer(palette="Set1")+
        scale_y_continuous(limits =c(0,3), breaks=seq(0,3, 0.5))+
        #scale_y_reverse()
        theme_bw()+
        labs(x="Reward Amount", y="Average Ranking")

## BY EXPECTATION CATEGORY SEPARATING EXPECTATIONS
data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("r_type", "r_amount", "tot_exp1", "tot_exp2"))

exp_df<-data %>% mutate(cat.exp1 = ifelse(tot_exp1 < 4.5, 
                "Low Expecations","High Expectations"),
                        cat.exp2 = ifelse(tot_exp2 < 4.5, 
                "Low Expectations","High Expectations"))
exp_df$variable <- factor(exp_df$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))

# Expectations sharing with one friend
avg_rank1<-exp_df %>% group_by(variable,r_amount, cat.exp1) %>%
        summarise(rank=mean(value))

ggplot(avg_rank1, aes(x=r_amount, y=rank, fill=r_amount) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid( cat.exp1~ variable )+
        scale_fill_brewer(palette="Set1")+
        scale_y_continuous(limits =c(0,3), breaks=seq(0,3, 0.5))+
        theme_bw()+
        labs(x="Reward Amount", y="Average Ranking")


# Expectations sharing with two friends
avg_rank2<-exp_df %>% group_by(variable,r_amount, cat.exp2) %>%
        summarise(rank=mean(value))

ggplot(avg_rank2, aes(x=r_amount, y=rank, fill=r_amount) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid( cat.exp2~ variable )+
        scale_fill_brewer(palette="Set1")+
        scale_y_continuous(limits =c(0,3), breaks=seq(0,3, 0.5))+
        theme_bw()+
        labs(x="Reward Amount", y="Average Ranking")


```

#2- REWARD TYPE (Product vs Cash)

Significant differences were found in terms of the type of reward (Cash or product) among the participants who preferred to share their reward (minority). 

### 2.1- FUNCTION calculating t.tests between REWARD TYPE(prod./cash)
```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}
t<-lapply(final_df[,c(2:12,31:33)], 
          function(x) t.test(x ~ final_df[,30], var.equal = TRUE))

ps<-data.frame(p.value = sapply(t, getElement, name = "p.value"))
format(ps, scientific = FALSE) 
```

###2.2- FUNCTION calculating Mann-Whitney (Non-Parametric) comparing REWARD TYPE(prod./cash)
```{r, echo=FALSE, eval=TRUE, include=TRUE ,cache=TRUE}
t<-lapply(final_df[,c(2:12,31:33)], 
          function(x) wilcox.test(x ~ final_df[,30], var.equal = TRUE))

ps<-data.frame(p.value = sapply(t, getElement, name = "p.value"))
format(ps, scientific = FALSE) 
```

### 2.3a TYPE OF REWARD and amount of friends to share the reward with.

Rewards in the form of Products were favoured when they were no shared with anyone, or shared with two friends. Moreover, when the reward was shared with only one friend people prefered to have Cash as a reward. 

```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

g2data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("r_type", "r_amount"))

pct2 <- g2data %>% 
  group_by(variable,r_type,value) %>% 
  summarise(n=n()) %>% 
  group_by(variable) %>% 
  mutate(perc=100*n/sum(n))

pct2$variable <- factor(pct2$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))

names(pct2)[2]<-c("Reward")

ggplot(pct2, aes(x=value, y=perc, fill=Reward) )+
        geom_bar(stat="identity",position="dodge")+
        ylab("percent") + 
        facet_grid(~ variable, margins=TRUE)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        labs(x="Schemes Ranking", y="Percentage from the total of each alternative")

#dev.copy(jpeg,"figures/prueba2.jpeg")
#dev.off()

```

### 2.3b TYPE OF REWARD and average RANKING.


```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

g2data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("r_type", "r_amount"))

avg_rank<-g2data %>% group_by(variable,r_type) %>%
        summarise(rank=mean(value))
avg_rank2<-g2data %>% group_by(variable,r_type, r_amount) %>%
        summarise(rank=mean(value))

ggplot(avg_rank, aes(x=r_type, y=rank, fill=r_type) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid(~ variable)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        labs(x="Reward Type", y="Average Ranking")

ggplot(avg_rank2, aes(x=r_type, y=rank, fill=r_type) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid(variable ~ r_amount)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        labs(x="Reward Type", y="Average Ranking")

#dev.copy(jpeg,"figures/prueba2.jpeg")
#dev.off()

```

### 2.4- Expectations about friends reactions and TYPE OF REWARD.

No differences were found in terms of the expactations about friends' reactions based on the TYPE OF REWARD. 

```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

gdata<-melt(final_df, measure.var= c("tot_exp1", "tot_exp2" ), 
         id.var = c("r_type", "r_amount"))

gdata$variable <- factor(gdata$variable,
                labels = c("1 Friend", "2 Friends"))
names(gdata)[1]<-"Reward"

ggplot(gdata, aes(x=variable, y=value, fill=Reward))+
        #geom_bar(stat="summary", fun.y="mean", position="dodge")+ 
        geom_boxplot(size = .75, position="dodge") +
        geom_jitter(alpha = .5)+
        scale_y_continuous(limits =c(0,9.1), breaks=seq(0,9, 0.5))+
        scale_fill_brewer(palette="Set1")+
        labs(x="Numbers of Friends to share the reward with", 
                y="Score-Expectations about friend's reaction")+
        theme_bw()

#dev.copy(jpeg,"figures/prueba2.jpeg")
#dev.off()
```

##3- Expectations about friends' reactions

###3.1.a-Schemes Ranking and expectation about friends' reactions

Overall, when expectations about friends' reactions was more negative, people preferred to choose the store were they keep all the reward. 

```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

gdata1<-melt(final_df, measure.var= c("tot_exp1","tot_exp2"), id.var = c("vd_0f","vd_1f","vd_2f"))

gdata2<-melt(gdata1, measure.var= c("vd_0f","vd_1f","vd_2f"), id.var = c("value", "variable"))

names(gdata2)[3:4]<-c("Group", "Ranking")

gdata2$Group <- factor(gdata2$Group, labels = 
                c("0 Ppl.", "1 Pers.", "2 Ppl."))
gdata2$variable <- factor(gdata2$variable, labels = 
                c("Expect.Sharing- 1 person", 
                  "Expect.Sharing- 2 people"))

ggplot(gdata2, aes(x=Group, y=value, fill=factor(Ranking)))+
        geom_boxplot(size = .75, position="dodge") +
        geom_jitter(alpha = .1)+
        scale_y_continuous(limits =c(0.5,9.1), breaks=seq(0.5,9,1))+
        scale_fill_brewer(palette="Set1", 
                          guide=guide_legend(title = "Rank"))+
        facet_grid(~ variable, margins=TRUE)+
        labs(x="Numbers of Friends to share the reward with", 
                y="Score-Expectations about friend's reaction")+
        #guide_legend(title = "Testing")+
        theme_bw()

#dev.copy(jpeg,"figures/prueba2.jpeg")
#dev.off()
```

***
The next two plots show that the differences in terms of friend's expectations were only observed between REWARD AMOUNT but not in terms of TYPE OF REWARD.

###3.1.b-Schemes AVERAGE Ranking and expectation about friends' reactions


```{r, echo=FALSE, eval=FALSE, include=TRUE, cache=TRUE}

gdata1<-melt(final_df, measure.var= c("tot_exp1","tot_exp2"), id.var = c("vd_0f","vd_1f","vd_2f"))

gdata2<-melt(gdata1, measure.var= c("vd_0f","vd_1f","vd_2f"), id.var = c("value", "variable"))

names(gdata2)[3:4]<-c("Group", "Ranking")

gdata2$Group <- factor(gdata2$Group, labels = 
                c("0 Ppl.", "1 Pers.", "2 Ppl."))
gdata2$variable <- factor(gdata2$variable, labels = 
                c("Expect.Sharing- 1 person", 
                  "Expect.Sharing- 2 people"))

avg_rank<-gdata2 %>% group_by(variable,Group) %>%
        summarise(avg=mean(value, Ranking))

ggplot(avg_rank, aes(x=Group, y=avg, fill=factor(variable)))+
        geom_bar(stat = "identity", position="dodge") +
        #geom_jitter(alpha = .1)+
        #scale_y_continuous(limits =c(0.5,9.1), breaks=seq(0.5,9,1))+
        scale_fill_brewer(palette="Set1", 
                          guide=guide_legend(title = "Rank"))+
        facet_grid(~ variable, margins=FALSE)+
        labs(x="Numbers of Friends to share the reward with", 
                y="Score-Expectations about friend's reaction")+
        #guide_legend(title = "Testing")+
        theme_bw()

ggplot(gdata2, aes(x=Group, y=value, fill=factor(Ranking)))+
        geom_bar(stat="identity", position="dodge") +
        #geom_jitter(alpha = .1)+
        #scale_y_continuous(limits =c(0.5,9.1), breaks=seq(0.5,9,1))+
        scale_fill_brewer(palette="Set1", 
                          guide=guide_legend(title = "Rank"))+
        facet_grid(~ variable, margins=FALSE)+
        labs(x="Numbers of Friends to share the reward with", 
                y="Score-Expectations about friend's reaction")+
        theme_bw()

#dev.copy(jpeg,"figures/prueba2.jpeg")
#dev.off()
```


###3.2-Schemes Ranking, Type of rewards and expectation about friends reactions when sharing with 2 PEOPLE

```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

long_data<-melt(final_df, measure.var= c("vd_0f","vd_1f","vd_2f"), 
         id.var = c("r_type", "r_amount", "tot_neg_eval", "tot_exp1", "tot_exp2"))

ggplot(long_data, aes(x = factor(value), y = tot_exp2)) +
  geom_boxplot(size = .75) +
  geom_jitter(alpha = .5) +
  facet_grid( r_type ~ r_amount, margins = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  labs(x="Schemes Ranking", y="Expectations-sharing with 2 friends")

#dev.copy(jpeg,"figures/prueba2.jpeg")
#dev.off()
```

###3.3-Schemes Ranking, Type of rewards and expectation about friends reactions when sharing with 1 Person

```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

long_data<-melt(final_df, measure.var= c("vd_0f","vd_1f","vd_2f"), 
         id.var = c("r_type", "r_amount", "tot_neg_eval", "tot_exp1", "tot_exp2"))

ggplot(long_data, aes(x = factor(value), y = tot_exp1)) +
  geom_boxplot(size = .75) +
  geom_jitter(alpha = .5) +
  facet_grid( r_type ~ r_amount, margins = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  labs(x="Schemes Ranking", y="Expectations-sharing with 1 PERSON")


#dev.copy(jpeg,"figures/prueba2.jpeg")
#dev.off()
```

#4- Fears of Negative Evaluation Scale

###4.1- Answers distribution.
No clear differences in the scale of Fears of Negative Evaluation were found when considering variables like size of the reward, type of reward, among others. 

```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=FALSE}

names(final_df)[30]<-"Reward"

ggplot(final_df, aes(tot_neg_eval, fill=Reward))+
        geom_histogram(colour="black", binwidth=0.3)+
        scale_fill_brewer(palette="Set1")+
        facet_grid( Reward ~ r_amount, margins = FALSE) +
        labs(x="Score - Fears of Negative Evaluations", y="Frequancy")+
        theme_bw()

```

### 4.2 Fears of negatives evaluations, AGE and GENDER
Younger people and Females have a tendency to have higher fears of Negative Evaluations. 

```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=FALSE}

ggplot(final_df, aes(x=tot_neg_eval, y=age, color=gender)) +
        geom_point(shape=16, size = I(5), alpha = I(0.4)) +
        scale_colour_hue(l=50) + # darker
        geom_smooth(method=lm,size=1) +
        labs(x="Scale - Fears of Negative Evaluations", y="Age")+
        scale_y_continuous(limits =c(10,90), breaks=seq(10,90,10))+
        theme_bw()

#dev.copy(jpeg,"figures/prueba2.jpeg")
#dev.off()
```


##5- Correlations Matrix

***
The strongest and most relevant correlations were between:

* Expect.Reaction_1 Friend -- Gender (-)
* Expect.Reaction_2 Friends -- Gender (-)
* Expect.Reaction_2 Friends -- Choice not sharing with Friends (-)
* Expect.Reaction_2 Friends -- Choice sharing with 2 Friends (+)
* Expect.Reaction_tOTAL -- Choice not sharing with Friends (-)
* Fear Neg. Evaluation -- Gender (+)
* Fear Neg. Evaluation -- Age (-)

***


###5.1- Pearson
```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=FALSE}

rxy<- select(final_df, tot_exp1,tot_exp2,exp_all, tot_neg_eval, 
           vd_0f, vd_2f, vd_1f, gender, income, age, employ)

rxy[1:ncol(rxy)] <- lapply(rxy[1:ncol(rxy)], function(x) as.numeric(x))

rxy<-as.matrix(rxy) 
rcorr(rxy, type="pearson")                           

```
###5.2- Spearman
```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}
rxy<- select(final_df, tot_exp1,tot_exp2,exp_all,tot_neg_eval, 
            vd_0f, vd_2f, vd_1f, gender, income, age, employ)

rxy[1:ncol(rxy)] <- lapply(rxy[1:ncol(rxy)], function(x) as.numeric(x))

rxy<-as.matrix(rxy)   
rcorr(rxy, type="spearman")                           
```


##6-Additional Demographics 

###6.1- Employment / Scheme preferences
```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("employ"))

fr1 <- data %>% 
        group_by(variable,employ,value) %>% 
        summarise(n=n()) 
fr2 <- fr1 %>% 
        group_by(employ, variable) %>% 
        summarise(n=sum(n))
pct <- left_join(fr1, fr2, by = c("employ"="employ", 
                                  "variable"="variable")) %>%
        mutate(perc=100*n.x/(n.y)) 


pct$variable <- factor(pct$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))
pct$value <- factor(pct$value)

names(pct)[2]<-"employ"

ggplot(pct, aes(x=value, y=perc, fill=variable) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid(~ employ)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        labs(x="Schemes Rankings", y="Percentage from the total of each alternative")

#dev.copy(jpeg,"figures/prueba2.jpeg")
#dev.off()

```


###6.2- Income / Scheme preferences
```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("income"))


fr1 <- data %>% 
        group_by(variable,income,value) %>% 
        summarise(n=n()) 
fr2 <- fr1 %>% 
        group_by(income, variable) %>% 
        summarise(n=sum(n))
pct <- left_join(fr1, fr2, by = c("income"="income", 
                                  "variable"="variable")) %>%
        mutate(perc=100*n.x/(n.y)) 

pct$variable <- factor(pct$variable, 
                labels = c("NO Friend", "1 Friend", "2 Friends"))
pct$value <- factor(pct$value) 

names(pct)[2]<-"income"

ggplot(pct, aes(x=value, y=perc, fill=variable) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid(~ income)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        labs(x="Schemes Rankings", y="Percentage from the total of each alternative")

#dev.copy(jpeg,"figures/prueba2.jpeg")
#dev.off()

```

###6.3- Income / Scheme preferences (AVERAGE RANKING)
```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("income"))

avg_rank<-data %>% group_by(variable,income) %>%
        summarise(rank=mean(value))


ggplot(avg_rank, aes(x=variable, y=rank, fill=variable) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid(~ income)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        labs(x="Schemes Rankings", y="Percentage from the total of each alternative")

ggplot(avg_rank, aes(x=income, y=rank, fill=income) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid(~ variable)+
        scale_fill_brewer(palette="Set1")+
        theme_bw()+
        labs(x="Schemes Rankings", y="Percentage from the total of each alternative")

#dev.copy(jpeg,"figures/prueba2.jpeg")
#dev.off()

```


plot(predict(m7),residuals(m7))