---
title: "Incentives_Core_Analysis"
author: "Juan Carpio"
date: "22 January 2016"
output: html_document
---


```{r,echo=TRUE, eval=TRUE, include=FALSE, cache=FALSE}
# Reading Clean File and setting relevant libraries.

## Change working directory
setwd("C:/Users/K56CA/Dropbox/PhD/Experiments Incentives/Follow_Up_Incentives")

##Relevant libraries
library("Hmisc")
library("dplyr")
library("tidyr")
library("ggplot2")
library("reshape2")
library("leaps")
library("car")


## read raw_data
data_clean_imp<-read.csv("clean_data.csv")
## correcting ID veriable
data_clean<- mutate(data_clean_imp, ID= X+1) %>% 
        select(ID, everything(), -X)

##Define factor variables

data_clean$r_amount <- factor(data_clean$r_amount, levels = c(1,2),
                      labels = c("£2", "£5")) 

data_clean$r_type <- factor(data_clean$r_type, levels = c(1,2),
                    labels = c("Cash", "Product")) 

data_clean$gender <- factor(data_clean$gender, levels = c(1,2),
                    labels = c("Male", "Female"))

data_clean$income <- factor(data_clean$income, levels = c(1:5),
                    labels = c("< 15k", "15k-19k",
                               "20k-29k", "> 30k", "No.Ans")) 

data_clean$employ <- factor(data_clean$employ, levels = c(1:6),
                    labels = c("FT-Emp", "PT-Emp","Unempl.", 
                               "Stud.", "Retired","Other")) 


## Adding totals for Measures: Neg.Evaluations and Expectations 

expect_1<-c("exp_x1_K","exp_x1_T", "exp_x1_S.R","exp_x1_G")
expect_2<-c("exp_x2_K","exp_x2_T", "exp_x2_S.R","exp_x2_G")
expect_all<-c("exp_x1_K","exp_x1_T", "exp_x1_S.R","exp_x1_G",
              "exp_x2_K","exp_x2_T", "exp_x2_S.R","exp_x2_G")
neg_eval<-c("neg.ev_1","neg.ev_2.R","neg.ev_3","neg.ev_4.R",
            "neg.ev_5","neg.ev_6","neg.ev_7.R","neg.ev_8",
            "neg.ev_9","neg.ev_10.R", "neg.ev_11","neg.ev_12")

final_df<-data_clean %>% mutate(
        tot_exp1 = rowMeans(.[expect_1]),
        tot_exp2 = rowMeans(.[expect_2]),
        exp_all = rowMeans(.[expect_all]),
        tot_neg_eval = rowMeans(.[neg_eval])
        )  

#final_df %>% group_by(r_amount) %>% summarise(avg = mean(age))

# Code to audit cases ###################
# final_df %>% filter(ID==315) %>% gather()
#########################################

```

## CHI SQUARE FIRST CHOICE
More than 80% prefered not to share the rward with anyone as a first choice. Such difference was highly significant. 
```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=FALSE}

long_data<-melt(final_df, measure.var= c("vd_0f","vd_1f","vd_2f"),
        id.var = c("ID","r_type", "r_amount", "tot_neg_eval",
                   "tot_exp1","tot_exp2", "exp_all")) 

chi_data<- filter(long_data, value==1)

#Summarise first choice frequencies and proportions
fr<-as.matrix(table(chi_data$variable))
p <- c(fr[1,1]/nrow(chi_data), fr[2,1]/nrow(chi_data),
                fr[3,1]/nrow(chi_data)) 

#calculating chi square
fr
p
chisq.test(fr)

```

###**Model Estimation -Function 
Takes a given multinomial model an return a table with all relevant values, including Likelihood Ratio test. 
```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=FALSE}

mod_frame <- function(m){
        
        mod<-summary(m)
        n<-length(mod$coefficients[1,])*2
   #Estimate Table values        
        coef<-matrix(cbind(mod$coefficients[1,],
                   mod$coefficients[2,]),n ,1)
        se<-matrix(cbind(mod$standard.errors[1,],
                 mod$standard.errors[2,]), n,1)
        z <-matrix(cbind(mod$coefficients[1,]/mod$standard.errors[1,],
                         mod$coefficients[2,]/mod$standard.errors[2,]))
        p <-((1 - pnorm(abs(z), 0, 1))*2)
        
        odds<- exp(coef)
       
        r.deviance<-mod$deviance
        AIC<-mod$AIC
        
        coef.name<-matrix(rep(mod$vcoefnames,2),n,1)
        cond<- matrix(cbind(rep(c("1_Friend"),n/2),
                        rep(c("2_Friends"),n/2)),n,1)
   #Build table        
                df<- as.data.frame(cbind(cond, coef.name)) %>% 
                cbind(round(cbind(coef,se,z,p,odds),3))
                colnames(df)<-c("Condition","Variable","Coeff",
                        "Sd.Error","z.value", "p.value", "odds")
                print(mod$call)
                print(df)

   #Model goodness of fitness
                fit<-(cbind(r.deviance,AIC))
                colnames(fit)<-c("Residual Deviance","AIC")
                print(fit)
   #Likelihood Ratio Test
                print(Anova(m))
}

```

#1- First Choice preferences 

## 1.3- MULTINOMIAL REGRESSION (nnet package)
```{r, echo=FALSE, eval=TRUE, include=TRUE, cache=FALSE, message=FALSE}

library("nnet")# Multinomial regression


long_data<-melt(final_df, measure.var= c("vd_0f","vd_1f","vd_2f"),
        id.var = c("ID","r_type", "r_amount", "tot_neg_eval",
                   "tot_exp1","tot_exp2", "exp_all", "gender",
                   "income", "age", "employ")) 

mr_data<- filter(long_data, value==1)
mr_data[[3]]=as.factor(mr_data[[3]])

## MODELS
mod1<- multinom(variable ~ r_type + exp_all + income + 
                employ + r_amount + gender + tot_neg_eval
                ,data = mr_data)
mod2<-update(mod1, . ~ . - tot_neg_eval)
mod3<-update(mod2, . ~ . - gender)
mod4<-update(mod3, . ~ . - r_amount)
mod5<-update(mod4, . ~ . - employ)

#Additional models
mod6<-update(mod4, . ~ . - income)
mod7<-update(mod4, . ~ . - exp_all)


mod1x<- multinom(variable ~ r_type, data = mr_data)      #  0.0126 
mod2x<- multinom(variable ~ exp_all, data = mr_data)     #  0.1136
mod3x<- multinom(variable ~ income, data = mr_data)      #  0.03547 
mod4x<- multinom(variable ~ employ, data = mr_data)      #  0.3815 
mod5x<- multinom(variable ~ r_amount, data = mr_data)    #  0.6254  
mod6x<- multinom(variable ~ gender, data = mr_data)      #  0.6475
mod7x<- multinom(variable ~ tot_neg_eval, data = mr_data)#  0.727 


                                                  ##Res.Dev.   AIC
m1<- update(mod5, .~. + r_amount)                 #406.0627 438.0627
m2<- update(mod5, .~. + tot_neg_eval)             #407.5776 439.5776
m3<- update(mod5, .~. + gender)                   #407.0715 439.0715
m4<- update(mod5, .~. + age)                      #407.1102 439.1102
m5<- update(mod5, .~. + employ)                   #397.2083 445.2083
m6<- update(mod5, .~. + r_amount*exp_all)         #393.9693 429.9693
m7<- update(mod5, .~. + r_amount + r_amount*exp_all) # ""      ""

###
m8<- update(mod5, .~. + r_amount*exp_all-income)  #409.1858 429.1858 
m9<- update(m6, .~. + r_amount*r_type)            #393.2482 433.2482
m10<- update(m6, .~. + r_amount*r_type -r_amount) #401.7075 437.7075


m11<- update(mod5, .~.  + r_amount*exp_all - r_amount) 
m12<- update(m6, .~.  + exp_all*r_type) 

```

### PROBABILITY PLOT OF THE BEST PREDICTIVE MODEL (constant <15)
```{r}

v.r_type<-c("Cash", "Product")
v.exp_all<-c(1:9)
v.r_amount<-c("£2", "£5")
v.income<- factor(1, levels = c(1),labels = c("< 15k"))

dexp<-expand.grid(v.r_type, v.exp_all, v.r_amount, v.income)
colnames(dexp)<-c("r_type", "exp_all", "r_amount", "income")


## store the predicted probabilities for each value of ses and write
pp.exp <- cbind(dexp, predict(m12, newdata = dexp, 
                               type = "probs", se = TRUE))

## calculate the mean probabilities within each level of ses
by(pp.exp[, 5:7], pp.exp$r_type, colMeans)

## melt data set to long for ggplot2
lpp <- melt(pp.exp, id.vars = c("exp_all", "r_type",
                "income", "r_amount"), value.name = "probability")

head(lpp) # view first few rows

## plot predicted probabilities across write values for
## each level of ses facetted by program type

lpp2 <- lpp
#Change schems labels
levels(lpp2$variable)[levels(lpp2$variable)=="vd_0f"]<- "No Friends"
levels(lpp2$variable)[levels(lpp2$variable)=="vd_1f"]<- "1 Friend"
levels(lpp2$variable)[levels(lpp2$variable)=="vd_2f"]<- "2 Friend2"
#Change income label
levels(lpp2$income)[levels(lpp2$income)=="< 15k"]<- "Income= < 15k"

#Change reward amount label
levels(lpp2$r_amount)[levels(lpp2$r_amount)=="£2"]<- "Reward= £2"
levels(lpp2$r_amount)[levels(lpp2$r_amount)=="£5"]<- "Reward= £5"

head(lpp2, 3)


ggplot(lpp2, aes(x = exp_all, y = probability, colour = r_type)) +
        geom_line(size=1) +
        facet_grid(variable ~ r_amount*income, scales="free")+
        scale_color_manual(values=c("blue","red"),
                name="Reward Type") +
        scale_x_continuous(limits =c(1,9), breaks=seq(1,9,1))+
        labs(x="Expectations about friends reactions", 
                y="Choice probability")
 
```

### PROBABILITY PLOT OF THE BEST PREDICTIVE MODEL (Constant >30)
```{r}

v.r_type<-c("Cash", "Product")
v.exp_all<-c(1:9)
v.r_amount<-c("£2", "£5")
v.income<- factor(1, levels = c(1),labels = c("> 30k"))

dexp<-expand.grid(v.r_type, v.exp_all, v.r_amount, v.income)
colnames(dexp)<-c("r_type", "exp_all", "r_amount", "income")


## store the predicted probabilities for each value of ses and write
pp.exp <- cbind(dexp, predict(m6, newdata = dexp, 
                               type = "probs", se = TRUE))

## calculate the mean probabilities within each level of ses
by(pp.exp[, 5:7], pp.exp$r_type, colMeans)

## melt data set to long for ggplot2
lpp <- melt(pp.exp, id.vars = c("exp_all", "r_type",
                "income", "r_amount"), value.name = "probability")

head(lpp) # view first few rows

## plot predicted probabilities across write values for
## each level of ses facetted by program type

lpp2 <- lpp
#Change schems labels
levels(lpp2$variable)[levels(lpp2$variable)=="vd_0f"]<- "No Friends"
levels(lpp2$variable)[levels(lpp2$variable)=="vd_1f"]<- "1 Friend"
levels(lpp2$variable)[levels(lpp2$variable)=="vd_2f"]<- "2 Friends"
#Change income label
levels(lpp2$income)[levels(lpp2$income)=="> 30k"]<- "Income= > 30k"

#Change reward amount label
levels(lpp2$r_amount)[levels(lpp2$r_amount)=="£2"]<- "Reward= £2"
levels(lpp2$r_amount)[levels(lpp2$r_amount)=="£5"]<- "Reward= £5"

head(lpp2, 3)


ggplot(lpp2, aes(x = exp_all, y = probability, colour = r_type)) +
        geom_line(size=1) +
        facet_grid(variable ~ r_amount*income, scales="free")+
        scale_color_manual(values=c("blue","red"),
                name="Reward Type") +
        scale_x_continuous(limits =c(1,9), breaks=seq(1,9,1))+
        labs(x="Expectations about friends reactions", 
                y="Choice probability")
 
```

### PROBABILITY PLOT OF THE BEST PREDICTIVE MODEL (Constant 2 FRIENDS)
```{r}

v.r_type<-c("Cash", "Product")
v.exp_all<-c(1:9)
v.r_amount<-factor(1, levels = c(1),labels = c("£5"))
v.income<- c("< 15k", "15k-19k","20k-29k", "> 30k", "No.Ans")

dexp<-expand.grid(v.r_type, v.exp_all, v.r_amount, v.income)
colnames(dexp)<-c("r_type", "exp_all", "r_amount", "income")


## store the predicted probabilities for each value of ses and write
pp.exp <- cbind(dexp, predict(m7, newdata = dexp, 
                               type = "probs", se = TRUE))

## calculate the mean probabilities within each level of ses
by(pp.exp[, 5:7], pp.exp$r_type, colMeans)

## melt data set to long for ggplot2
lpp <- melt(pp.exp, id.vars = c("exp_all", "r_type",
                "income", "r_amount"), value.name = "probability")

head(lpp) # view first few rows

## plot predicted probabilities across write values for
## each level of ses facetted by program type

lpp2 <- lpp
#Change schems labels
levels(lpp2$variable)[levels(lpp2$variable)=="vd_0f"]<- "No Friends"
levels(lpp2$variable)[levels(lpp2$variable)=="vd_1f"]<- "1 Friend"
levels(lpp2$variable)[levels(lpp2$variable)=="vd_2f"]<- "2 Friend2"
#Change income label
levels(lpp2$income)[levels(lpp2$income)=="> 30k"]<- "Income= > 30k"

#Change reward amount label
levels(lpp2$r_amount)[levels(lpp2$r_amount)=="£2"]<- "Reward= £2"
levels(lpp2$r_amount)[levels(lpp2$r_amount)=="£5"]<- "Reward= £5"

head(lpp2, 3)


ggplot(lpp, aes(x = exp_all, y = probability, colour = variable)) +
        geom_line(size=1) +
        facet_grid( income~r_type)+#, scales="free"
        #scale_color_manual(values=c("blue","red"),
        #        name="Reward Type") +
        #scale_x_continuous(limits =c(1,9), breaks=seq(1,9,1))+
        labs(x="Expectations about friends reactions", 
                y="Choice probability")
 
```




### PROBABILITY PLOT OF THE BEST PREDICTIVE MODEL (expectations constant)

```{r}


v.r_type<-c("Cash", "Product")
v.exp_all<-c(7) #average value
v.r_amount<-c("£2", "£5")
v.income<- c("< 15k", "15k-19k","20k-29k", "> 30k", "No.Ans")

dexp<-expand.grid(v.r_type, v.exp_all, v.r_amount, v.income)
colnames(dexp)<-c("r_type", "exp_all", "r_amount", "income")


## store the predicted probabilities for each value of ses and write
pp.exp <- cbind(dexp, predict(m7, newdata = dexp, 
                               type = "probs", se = TRUE))

## calculate the mean probabilities within each level of ses
by(pp.exp[, 5:7], pp.exp$r_type, colMeans)

## melt data set to long for ggplot2
lpp <- melt(pp.exp, id.vars = c("exp_all", "r_type",
                "income", "r_amount"), value.name = "probability")

head(lpp) # view first few rows

## plot predicted probabilities across write values for
## each level of ses facetted by program type

lpp2 <- lpp
#Change schems labels
levels(lpp2$variable)[levels(lpp2$variable)=="vd_0f"]<- "No Friends"
levels(lpp2$variable)[levels(lpp2$variable)=="vd_1f"]<- "1 Friend"
levels(lpp2$variable)[levels(lpp2$variable)=="vd_2f"]<- "2 Friend2"

#Change reward amount label
levels(lpp2$r_amount)[levels(lpp2$r_amount)=="£2"]<- "Reward= £2"
levels(lpp2$r_amount)[levels(lpp2$r_amount)=="£5"]<- "Reward= £5"

head(lpp2, 3)


ggplot(lpp2, aes(x = income, y = probability,
                colour = r_type, group=r_type)) +
                geom_line()+
                geom_point() + 
                facet_grid(variable ~ r_amount, scales="free")+
                        scale_color_manual(values=c("blue","red"),
                        name="Reward Type") +
                theme(axis.text.x= element_text(angle = 90, hjust = 1))
                labs(x="Income Category", y="Choice probability")
 
```



## Modelling with income as a rank

```{r}

long_data<-melt(final_df, measure.var= c("vd_0f","vd_1f","vd_2f"),
        id.var = c("ID","r_type", "r_amount", "tot_neg_eval",
                   "tot_exp1","tot_exp2", "exp_all", "gender",
                   "income", "age", "employ")) 

long_data2<- long_data %>% filter(income!="No.Ans") 
        
mr_data<- filter(long_data, value==1)
mr_data[[3]]=as.factor(mr_data[[3]])#ordered
mr_data[[9]]=ordered(mr_data[[9]])

## MODELS
mod1<- multinom(variable ~ r_type + exp_all + income + 
                employ + r_amount + gender + tot_neg_eval
                ,data = mr_data)
mod2<-update(mod1, . ~ . - tot_neg_eval)
mod3<-update(mod2, . ~ . - gender)
mod4<-update(mod3, . ~ . - r_amount)
mod5<-update(mod4, . ~ . - employ)

#Additional models
mod6<-update(mod4, . ~ . - income)
mod7<-update(mod4, . ~ . - exp_all)


mod1x<- multinom(variable ~ r_type, data = mr_data)      #  0.0126 
mod2x<- multinom(variable ~ exp_all, data = mr_data)     #  0.1136
mod3x<- multinom(variable ~ income, data = mr_data)      #  0.03547 
mod4x<- multinom(variable ~ employ, data = mr_data)      #  0.3815 
mod5x<- multinom(variable ~ r_amount, data = mr_data)    #  0.6254  
mod6x<- multinom(variable ~ gender, data = mr_data)      #  0.6475
mod7x<- multinom(variable ~ tot_neg_eval, data = mr_data)#  0.727 


                                                  ##Res.Dev.   AIC
m1<- update(mod5, .~. + r_amount)                 #406.0627 438.0627
m2<- update(mod5, .~. + tot_neg_eval)             #407.5776 439.5776
m3<- update(mod5, .~. + gender)                   #407.0715 439.0715
m4<- update(mod5, .~. + age)                      #407.1102 439.1102
m5<- update(mod5, .~. + employ)                   #397.2083 445.2083
m6<- update(mod5, .~. + r_amount*exp_all)         #393.9693 429.9693
m7<- update(mod5, .~. + r_amount + r_amount*exp_all) # ""      ""

###
m8<- update(mod5,.~. +r_amount+r_amount*exp_all-income)
                                                  #409.1858 429.1858 
m9<- update(m6, .~. + r_amount*r_type)            #393.2482 433.2482
m10<- update(m6, .~. + r_amount*r_type -r_amount) #401.7075 437.7075


m11<- update(mod5, .~.  + r_amount*exp_all - r_amount) 



```

## REWARD AMOUNT AND EXPECTATIOS SHARING WITH 1 FRIEND
```{r,echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}


low.exp_df<-final_df %>% filter(tot_exp1 <= 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_amount)

high.exp_df<-final_df %>% filter(tot_exp1 > 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_amount)


u.low<-lapply(low.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~low.exp_df[,4],var.equal= TRUE))

u.high<-lapply(high.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~high.exp_df[,4],var.equal= TRUE))

```

## REWARD AMOUNT AND EXPECTATIOS SHARING WITH 2 FRIENDS (considering rankings)
```{r,echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}


low.exp_df<-final_df %>% filter(tot_exp2 <= 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_amount)

high.exp_df<-final_df %>% filter(tot_exp2 > 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_amount)


u.low.2f<-lapply(low.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~low.exp_df[,4],var.equal= TRUE))

u.high.2f<-lapply(high.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~high.exp_df[,4],var.equal= TRUE))

```


## Reward Amount and expectations about friends' reactions. 
```{r,echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

#Median
final_df %>% select(tot_exp1, tot_exp2, r_amount) %>%
                group_by(r_amount) %>%
                summarise(median(tot_exp1),median(tot_exp2), 
                          mean(tot_exp1),mean(tot_exp2))


# Mann Whitney U-Test
u<-lapply(final_df[,c(31:33)], 
          function(x) wilcox.test(x ~ final_df[,29], var.equal= FALSE))


```

## PLOT REWARD AMOUNT AND EXPECTATIOS FRIENDS REACTIONS
```{r,echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}
gdata<-melt(final_df, measure.var= c("tot_exp1", "tot_exp2" ), 
         id.var = c("r_type", "r_amount"))

gdata$variable <- factor(gdata$variable,
                labels = c("1 Friend", 
                          "2 Friends"))
names(gdata)[2]<-"Reward"


ggplot(gdata, aes(x=variable, y=value, fill=Reward))+
        geom_bar(stat = "summary", fun.y = "mean",position="dodge")+
        scale_y_continuous(limits =c(0,9), breaks=seq(0,9,1))+
        scale_fill_brewer(palette="Set1")+
        labs(x="Number of friends with which the reward would be shared",
                y="Score-Expectations about friend's reaction")+
        theme_bw()
```


##Scheme rankings and Reward Framing
```{r,echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

#Means
final_df %>% select(vd_0f, vd_1f, vd_2f, r_type) %>%
                group_by(r_type) %>%
                summarise(mean(vd_0f),mean(vd_1f),mean(vd_2f))                  


# Mann Whitney U-Test
u<-lapply(final_df[,c(2:4)], 
          function(x) wilcox.test(x ~ final_df[,30], var.equal= FALSE))

ps<-data.frame(p.value = sapply(u, getElement, name = "p.value"))
format(ps, scientific = FALSE)

## Plot

data<-melt(final_df, measure.var= c("vd_0f","vd_1f", "vd_2f"), 
         id.var = c("r_type", "r_amount", "tot_exp1", "tot_exp2"))

avg_rank<-data %>% group_by(variable,r_type) %>%
        summarise(rank=mean(value))

avg_rank$variable <- factor(avg_rank$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))
names(avg_rank)[2]<-c("Framing")

ggplot(avg_rank, aes(x=Framing, y=rank, fill=Framing) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid(~ variable)+
        scale_fill_brewer(palette="Set1")+
        scale_y_continuous(limits =c(0,3), breaks=seq(0,3, 0.5))+
        theme_bw()+
        labs(x="Reward Framing", y="Average Ranking")
######
exp_df<-data %>% mutate(cat.exp1 = ifelse(tot_exp1 < 4.5, 
                "Low Expecations","High Expectations"),
                        cat.exp2 = ifelse(tot_exp2 < 4.5, 
                "Low Expectations","High Expectations"))
exp_df$variable <- factor(exp_df$variable,
                labels = c("NO Friend", "1 Friend", "2 Friends"))

# Expectations sharing with one friend
avg_rank1<-exp_df %>% group_by(variable,r_type, cat.exp1) %>%
        summarise(rank=mean(value))
names(avg_rank1)[2]<-c("Framing")

ggplot(avg_rank1, aes(x=Framing, y=rank, fill=Framing) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid( cat.exp1~ variable )+
        scale_fill_brewer(palette="Set1")+
        scale_y_continuous(limits =c(0,3), breaks=seq(0,3, 0.5))+
        theme_bw()+
        labs(x="Reward Amount", y="Average Ranking")

# Expectations sharing with two friends
avg_rank2<-exp_df %>% group_by(variable,r_type, cat.exp2) %>%
        summarise(rank=mean(value))
names(avg_rank2)[2]<-c("Framing")

ggplot(avg_rank2, aes(x=Framing, y=rank, fill=Framing) )+
        geom_bar(stat="identity",position="dodge")+
        facet_grid( cat.exp2~ variable )+
        scale_fill_brewer(palette="Set1")+
        scale_y_continuous(limits =c(0,3), breaks=seq(0,3, 0.5))+
        theme_bw()+
        labs(x="Reward Amount", y="Average Ranking")


```

## REWARD framing (type) AND EXPECTATIOS SHARING WITH 1 FRIEND
```{r,echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}


low.exp_df<-final_df %>% filter(tot_exp1 <= 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_type)

high.exp_df<-final_df %>% filter(tot_exp1 > 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_type)


u.low.1f<-lapply(low.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~low.exp_df[,4],var.equal= TRUE))

u.high.1f<-lapply(high.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~high.exp_df[,4],var.equal= TRUE))

```


## REWARD FRAMING (TYPE) AND EXPECTATIOS SHARING WITH 2 FRIENDS (considering rankings)
```{r,echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}


low.exp_df<-final_df %>% filter(tot_exp2 <= 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_type)

high.exp_df<-final_df %>% filter(tot_exp2 > 4.5) %>%
        select(vd_0f, vd_1f, vd_2f, r_type)


u.low.2f<-lapply(low.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~low.exp_df[,4],var.equal= TRUE))

u.high.2f<-lapply(high.exp_df[,c(1:3)], 
          function(x) wilcox.test(x ~high.exp_df[,4],var.equal= TRUE))

```

## Reward Framing and expectations about friends' reactions. 
```{r,echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}

#Median
final_df %>% select(tot_exp1, tot_exp2, r_type) %>%
                group_by(r_type) %>%
                summarise(median(tot_exp1),median(tot_exp2), 
                          mean(tot_exp1),mean(tot_exp2))

# Mann Whitney U-Test
u<-lapply(final_df[,c(31:33)], 
          function(x) wilcox.test(x ~ final_df[,30], var.equal= FALSE))
ps<-data.frame(p.value = sapply(u, getElement, name = "p.value"))
format(ps, scientific = FALSE)

```


## PLOT REWARD FRAMING AND EXPECTATIOS FRIENDS REACTIONS
```{r,echo=FALSE, eval=TRUE, include=TRUE, cache=TRUE}
gdata<-melt(final_df, measure.var= c("tot_exp1", "tot_exp2" ), 
         id.var = c("r_type", "r_amount"))

gdata$variable <- factor(gdata$variable,
                labels = c("1 Friend", 
                          "2 Friends"))
names(gdata)[1]<-"Framing"


ggplot(gdata, aes(x=variable, y=value, fill=Framing))+
        geom_bar(stat = "summary", fun.y = "mean",position="dodge")+
        scale_y_continuous(limits =c(0,9), breaks=seq(0,9,1))+
        scale_fill_brewer(palette="Set1")+
        labs(x="Number of friends with which the reward would be shared",
                y="Score-Expectations about friend's reaction")+
        theme_bw()

```
